### 2018-01-05 includes/abstract.tex
Added paragraph stubs.

    Many SMT solvers that support the theory of strings have been developed over the past decade, and several have matured to the point of being performant and practically useful. Moreover a standard input language, SMT-LIB, has been developed, and many mature solvers support it. In this paper we present StringFuzz, a fuzzer and problem generator for string solvers. With it we analyse four mature string solvers: Z3str3, Norn, CVC4, and ABC. We use it to craft inputs that elicit poor performance in Z3str3 and CVC4, and present algorithmic improvements to mitigate it. Finally, we present several minor bugs in Z3str3 that were exposed by StringFuzz.

>>>>

    In this paper we present StringFuzz: an SMT-LIB problem fuzzer and generator for string solvers. With it we analyse \numSolvers{} mature string solvers: \theSolvers{}. We use it to craft inputs that elicit poor performance in Z3str3 and CVC4, and provide analyses of the causes of the performance degradations. Our experimental data suggest that there are classes of problems that will always be hard for Z3str3 and easy for CVC4, and vice versa, due to the limitations of the core algorithms implemented by those solvers. We also present several minor bugs in Z3str3 that were exposed by StringFuzz. Finally, we provide a rich repository of problems in SMT-LIB format, generated both by StringFuzz and by hand, to encourage other solver authors to likewise improve their solvers.
